Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-23 WSSSPE2_report/WSSSPE2_review.tex
Section 3.2: temp fix for compilation errors.
Section 3: A handful minor changes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynotes} \label{sec:keynotes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{\footnotesize{Lead: Choi. Volunteers contact lead. Live notes: \href{http://tinyurl.com/q6ew45v}{Google Notes}}.
%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing
Abstracts: \href{http://tinyurl.com/mnenzms}{WSSSPE2}. Slides: \href{http://tinyurl.com/las8tsq}{here}.}

@@

Thaney introduced Mozilla's Software Discovery
Index\footnote{\url{http://softwarediscoveryindex.org/report/}}, which
identifies scientific software by archiving and standardizing metadata for
software and hence help connect both developers and users. Ted Habermann in the
audience commented that if the metadata is minimal, it would be less onerous for
data providers, but more burdensome for users---it could be challenging to keep
a balance between what have to be captured and what would be ideal if we do not
want to lose user engagement as in the case of the old Harvard Dataverse, finding often
only the first four fields of three pages of metadata were filled out.

@@

\todo{Slides: \url{http://tinyurl.com/pd9tmh3}}

In a recent survey of UK research-intensive universities, 92\% of researchers
said they used research software and 68\% said their research would be impossible
without software. Yet 71\% have had no formal software training, and few are
ready to apply many of the things we take for granted such as testing or
virtualisation. WSSSPE represents the pinnacle of what we understand to be the
best practice around scientific software in our community. My talk will
challenge the workshop participants to come up with ways of taking this best
practice to those 92\% of researchers in a way that will lead to maximum benefit
to the scientific community.

@@

We do not recognise these hundreds of thousands of researchers because we think
they are the long tail and forget that they are the mainstream and we are the
elite minority

@@

Survey of  PhD students from Russell Group university conducted by SSI between Aug - Sep 2014.
~100 respondents covering representative range of discipline.

@@

Investment in 2013-2014 financial year, an amount that has risen by
3\% on average over last four years

@@

\begin{verbatim}
Source: The Scientific Century, Royal Society, 2010 (revised to reﬂect ﬁrst stage
clariﬁcaFon from ``What Do PhD’s Do?'' study)
\end{verbatim}

@@

\url{http://dx.doi.org/10.6084/m9.ﬁgshare.1243288}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynotes} \label{sec:keynotes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{\footnotesize{Lead: Choi. Live notes: \href{http://tinyurl.com/q6ew45v}{Google Notes} and \href{http://tinyurl.com/pd9tmh3}{here}}.
%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing
Abstracts: \href{http://tinyurl.com/mnenzms}{WSSSPE2}. Slides: \href{http://tinyurl.com/las8tsq}{here}.}

@@

Thaney introduced Mozilla's Software Discovery Index
(SDI)\footnote{\url{http://softwarediscoveryindex.org/report/}}, which
facilitates more efficient scientific research. SDI identifies scientific
software by archiving and standardizing metadata for software and hence help
connect both developers and users. Ted Habermann in the audience commented that
if the metadata is minimal, it would be less onerous for data providers, but
more burdensome for users---it could be challenging to keep a balance between
what have to be captured and what would be ideal if we do not want to lose user
engagement as in the case of the old Harvard Dataverse, finding often only the
first four fields of three pages of metadata were filled out.

@@

In a recent survey of UK research-intensive universities, 92\% of researchers
said they used research software and 68\% said their research would be impossible
without software. Yet 71\% have had no formal software training, and few are
ready to apply many of the things we take for granted such as testing or
virtualization. WSSSPE represents the pinnacle of what we understand to be the
best practice around scientific software in our community. My talk will
challenge the workshop participants to come up with ways of taking this best
practice to those 92\% of researchers in a way that will lead to maximum benefit
to the scientific community.

@@

We do not recognise these hundreds of thousands of researchers because we think
they are the long tail and forget that they are the mainstream and we are the
elite minority.

@@

Survey of  PhD students from Russell Group university conducted by SSI between Aug -- Sep 2014.
approximately 100 respondents covering representative range of discipline.

@@

Investment in 2013--2014 financial year, an amount that has risen by
3\% on average over last four years

@@

  \begin{comment}
Source: The Scientific Century, Royal Society, 2010 (revised to reﬂect ﬁrst stage
clariﬁcaFon from ``What Do PhD’s Do?'' study)

@@

\url{http://dx.doi.org/10.6084/m9.ﬁgshare.1243288}
\end{comment}
